	\chapter{Introduction}
	% Disease background
	\section{Schizophrenia}
	\Gls{scz} is a devastating psychiatric disorder affecting approximately $0.3\sim0.7\%$ of the population  worldwide \citep{AmericanPsychiatricAssociation2013}.
	Generally, the typical age of onset of \gls{scz} is around late adolescent or late 20s in male and late 20s or early 30s in female \citep{Schultz2007}.
	
	\input{lr_scz.tex}
	\input{lr_herit.tex}
	\input{lr_scz_gene.tex}
	\input{lr_ldsc.tex}
	%\input{lr_antipsychotics.tex}
	\section{Summary}
	To conclude, \glng{scz} is a complex disorder affecting approximately 1\% of the population worldwide. 
	It is now known that the disease is affected by a combination of genetic and environmental factors. 
	Therefore, to fully understand the disease mechanism for the development of proper treatments, it is important not only to examine how certain genetic polymorphisms can predispose individuals to the disease development, but also how environmental factors can act as a trigger for the disorder in apparently healthy individuals.  
	
	In this thesis, we would like to develop an algorithm for the estimation of \gls{SNP} heritability from \gls{GWAS} summary statistics that is robust to traits with different genetic architectures. 
	We would also like to investigate the effect of case control sampling and extreme phenotype sampling on the performance of \gls{ldsc}.
	On the other hand, as prenatal infection is the largest environmental risk for \glng{scz}, we would like to understand how prenatal infection triggers \glng{scz} through studying the change in global gene expressions in mice cerebellum.
	
	First, in \Cref{heritabilityChapter}, we performed a series of empirical simulations to assess the performance of \gls{ldsc} in the estimation of \gls{SNP} heritability. 
	We also proposed an alternative approach for the estimation of \gls{SNP}-heritability from \gls{GWAS} summary statistics that is robust to different genetic architectures.
	
	In \Cref{omegaProject}, a hypothesis generation study was performed to study the effect of \gls{mia} on the gene expression pattern of mouse cerebellum. 
	On top of that, as recent study suggested that n-3 \gls{pufa} rich diet can help to reduce the \glng{scz}-like behaviour observed mouse exposed to early \gls{mia} \citep{Li2015}, we also investigated the effect of n-3 \gls{pufa} rich diet on the gene expression pattern of mouse cerebellum.
	
	Lastly, we summarize and conclude all findings in \Cref{conclusionChapter} and give future perspectives on the \glng{szc} research.
	